04-analisis

### 2024-07-08 04-analisis.qmd
Ultimos cambios: paper, front matter, cover letter, back matter

---
author: "Equipo Edumer"
bibliography: "input/bib/just-ineq-merit.bib"
csl: "input/bib/apa6.csl"
---

@@

texreg::texreg(
  l = list(modelos_health[[2]], modelos_health[[3]], modelos_pension[[2]], modelos_pension[[3]], modelos_educ[[2]], modelos_educ[[3]]),
  caption = NULL,
  stars = c(0.05, 0.01, 0.001),
  custom.note = "\\item Note: Cells contain regression coefficients with standard errors in parentheses. Control variables are included. %stars \\\\ \\item Source: own elaboration based on First Study of Civic Education 2017.",threeparttable = T,
  custom.header = list("Health" = 1:2, "Pensions" = 3:4, "Education" = 5:6),
  custom.model.names = rep(c("Model 1", "Model 2"), 3),
  custom.coef.map = ccoef,
  leading.zero = TRUE,
  use.packages = FALSE,
  booktabs = TRUE,
  scalebox = 0.8,
  groups = list("Parental education (Ref.= Non-university)" = 6:7, "Socioeconomic level (Ref.= Low)" = 9:10, "Achievement score (Ref.= Low)" = 11:12),
  custom.gof.rows = list("Controls" = rep("Yes", 6)),
  include.loglik = FALSE,
  include.aic = FALSE,
)

@@

texreg::texreg(list(reg1_bienestar, reg2_bienestar, reg4_bienestar, reg5_bienestar),
                custom.model.names = c("Model 1",
                                       "Model 2",
                                       "Model 3",
                                       "Model 4"),
                caption = NULL,
                stars = c(0.05, 0.01, 0.001),
                custom.coef.map = ccoef,
               custom.note = "\\item Note: Cells contain regression coefficients with standard errors in parentheses. Control variables are included. %stars \\\\ \\item Source: own elaboration based on First Study of Civic Education 2017.",threeparttable = T,
                leading.zero = T,
                use.packages = F,
                booktabs = TRUE,
                scalebox = 0.85,
                groups = list("Parental education (Ref.= Non-university)" = 7:8,
                              "Socioeconomic level (Ref.= Low)" = 10:11,
                              "Achievement score (Ref.= Low)" = 12:13),
                custom.gof.rows = list("Controls"=rep("Yes",4),
                                       "Deviance" = c(deviance1,
                                                    deviance2,
                                                    deviance4,
                                                    deviance5),
                                       "Deviance Test (p)" = c(test.pvalues1,
                                                             test.pvalues2,
                                                             test.pvalues4,
                                                             test.pvalues5)),
                include.loglik = FALSE,include.aic = FALSE)

>>>>

---
author: "Equipo Edumer"
bibliography: "input/bib/just-ineq-merit.bib"
csl: "input/bib/multidisciplinary-digital-publishing-institute.csl"
---

@@

texreg::texreg(
  l = list(modelos_health[[2]], modelos_health[[3]], modelos_pension[[2]], modelos_pension[[3]], modelos_educ[[2]], modelos_educ[[3]]),
  caption = NULL,
  stars = c(0.05, 0.01, 0.001),
  custom.note = "\\item Note: Cells contain regression coefficients with standard errors in parentheses. Control variables are included. %stars \\\\ \\item Source: own elaboration based on First Study of Civic Education 2017.",threeparttable = T,
  custom.header = list("Health" = 1:2, "Pensions" = 3:4, "Education" = 5:6),
  custom.model.names = rep(c("Model 1", "Model 2"), 3),
  custom.coef.map = ccoef,
  leading.zero = TRUE,
  use.packages = FALSE,
  booktabs = TRUE,
  scalebox = 0.8,
  include.loglik = FALSE,
  include.aic = FALSE,
  groups = list("Parental education (Ref.= Non-university)" = 6:7, "Socioeconomic level (Ref.= Low)" = 9:10, "Achievement score (Ref.= Low)" = 11:12),
  custom.gof.names = c("BIC", 
                       "Num.obs",
                       "Num. groups: Schools",
                       "Var: Schools (Intercept)"),
  custom.gof.rows = list("Controls"=rep("Yes", 6))
)

@@

texreg::texreg(list(reg1_bienestar, reg2_bienestar, 
                       reg4_bienestar, reg5_bienestar),
               custom.model.names = c("Model 1",
                                      "Model 2",
                                      "Model 3",
                                      "Model 4"),
               caption = NULL,
               stars = c(0.05, 0.01, 0.001),
               custom.coef.map = ccoef,
               custom.note = "\\item Note: Cells contain regression coefficients with standard errors in parentheses. Control variables are included. %stars \\\\ \\item Source: own elaboration based on First Study of Civic Education 2017.",threeparttable = T,
               leading.zero = T,
               use.packages = F,
               booktabs = TRUE,
               scalebox = 0.85,
               include.loglik = FALSE,
               include.aic = FALSE,
               groups = list("Parental education (Ref.= Non-university)" = 7:8,
                             "Socioeconomic level (Ref.= Low)" = 10:11,
                             "Achievement score (Ref.= Low)" = 12:13),
               custom.gof.names = c("BIC", 
                                    "Num.obs",
                                    "Num. groups: Schools",
                                    "Var: Schools (Intercept)",
                                    "Var: Residual"),
               custom.gof.rows = list("Controls"=rep("Yes",4),
                                      "Deviance" = c(deviance1,
                                                     deviance2,
                                                     deviance4,
                                                     deviance5),
                                      "Deviance Test (p)" = c(test.pvalues1,
                                                              test.pvalues2,
                                                              test.pvalues4,
                                                              test.pvalues5))
               )
